### 2010-03-11 papers/icfp-2010-desc/paper_desc.tex
Desc@ICFP: close section Levitation.

\subsection{Examples}

@@

@@

\subsection{Fix-point}

@@

%% I'm kind of shafted (haha) by this:
%%     - We have not yet introduced tagged descriptions
%%     - Tagged descriptions are much more complex now
%%     - "cases.i" is a syntax I just made up
\[
\Rule{\forall e_i \in \vec{e}, \propag{\push{\descop{cases.i}{\Mu{(\DSigma{(\Enum\: \CN{const})}{\CN{cases}})}}}{e_i}}
                        {e'_i}}
     {\propag{\push{C\: \vec{e}}{\Mu{(\DSigma{(\Enum\: \CN{const})}{\CN{cases}})}}}
             {\Con{(\etag{C}, \widetilde{e'})}}}\;\etag{C} \in \CN{cases}
\]

>>>>

\subsection{Examples}
\label{sec:desc-examples}

@@

\begin{wstructure}
<- Tagged description
    <- Form TDesc = List (UId x Desc) [equation]
    <- Follow usual sums-of-product presentation of data-type
        <- Finite set of constructors
        <- Then whatever you want
    -> Any Desc data-type can be turned into this form
        -> No loss of expressive power
        /> Garantee a ``constructor form''
\end{wstructure}

From the examples above, we observe that data-types are defined by a
$\DSigma$ which first argument is a finite set of constructor. The
descriptions fitting into this pattern are called \emph{tagged}
description. Formally, we have:

\[
 \TagDesc \mapsto \SIGMA{\V{E}}{\EnumU} \spi{\V{E}}{\LAM{\_} \Desc}
\]

Again, this is a clear reminiscence of the ``sum-of-products'' style:
we have a finite sum of constructors. Of course, every description can
be expressed into this style, by using a singleton as single
constructor.

@@

\subsection{Fix-point}
\label{sec:desc-fix-point}

@@

%% I'm kind of shafted (haha) by this:
%%     - We have not yet introduced tagged descriptions
%%     - Tagged description in a Mu, that just doesn't work...
\[
\Rule{\forall e_i \in \vec{e}, \propag{\push{e_i}
                                            {\descop{f\: i}{(\Mu{(\DSigma{(\Enum\: b)}{f})})}}}
                                      {e'_i}}
     {\propag{\push{C\: \vec{e}}{\Mu{(\DSigma{(\Enum\: b)}{f})}}}
             {\Con{(\etag{C}, \widetilde{e'})}}}\;\etag{C} \in b
\]
